Multisensor Architecture for an Intersection Management System

### 2018-06-21 ch3-arch_sys.tex
Final draft

\subsection{Intersection monitoring Datasets}

@@

\item[camera\_background\_remove] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/camera_bg_remove.pdf}
\caption{camera\_background\_remove block}
\label{cam_bg_remove}
\end{figure}

@@

This block generates a occupancy grid based on cartesian data from laser. As parameters, this block receives a cell size for the grid, the laser configuration and the scene configuration. The grid size is of $N_C$ Columns and $N_R$ rows, obtained as follows:

@@

Then, the cells that form a straigh line between the cell of laser position and the cells of each laser measure, should be marked as empty. To get the list of these cells Bresenham's algorithm \todo{Check bresenham algorithm reference} is used. This algorithm is widely used in computer graphics due to it simplicity and because it uses integer arithmetics, making it computationally cheap.

The input of this algorithm is a pair of coordinates, the endpoints of the line, and as result, the set of points that completes the line between, is returned.

Now, the update procedure for the probability in each cell is described for the function $f$:

\todo{update policy}

\item[occgrid\_merge] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occgrid_merge.pdf}
\caption{occgrid\_merge}
\label{occgrid_merge}
\end{figure}

@@

@@

@@

\item[clusters\_to\_occupancy\_level] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
\caption{clusters\_to\_occupancy\_level}
\label{clusters_to_occupancy_level}
\end{figure}

@@

\item[occgrid\_to\_occupancy\_level] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
\caption{occgrid\_to\_occupancy\_level}
\label{occgrid_to_occupancy_level}
\end{figure}

@@

\item[vehicle\_counter\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
\caption{vehicle\_counter\_merge}
\label{vehicle_counter_merge}
\end{figure}

\item[occupancy\_level\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
\caption{occupancy\_level\_merge}
\label{occupancy_level_merge}
\end{figure}

@@

\item[laser\_publisher] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/laser_publisher.pdf}
\caption{laser\_publisher}
\label{laser_publisher}
\end{figure}

\item[camera\_publisher] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
\caption{camera\_publisher}
\label{camera_publisher}
\end{figure}

\item[dataset\_control] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/dataset_ctrl.pdf}
\caption{dataset\_control}
\label{dataset_control}
\end{figure}

@@

>>>>

\subsection{Intersection monitoring Datasets} \label{possi_ds}

@@

%\item[camera\_background\_remove] \hfill
%
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/camera_bg_remove.pdf}
%\caption{camera\_background\_remove block}
%\label{cam_bg_remove}
%\end{figure}

@@

This block generates a occupancy grid based on cartesian data from laser sensors. The cartesian data received from sensors is merged in a timeslot basis, filling a buffer for each sensor and processing available data using a defined period $T_{om}$. As parameters, this block receives a cell size for the grid, the laser sensors configuration and the scene configuration. The grid size is of $N_C$ Columns and $N_R$ rows, obtained as follows:

@@

Then, the cells that form a straigh line between the cell of laser position and the cells of each laser measure, should be marked as empty. To get the list of these cells Bresenham's algorithm is used. This algorithm is widely used in computer graphics due to it simplicity and because it uses integer arithmetics, making it computationally cheap. The input of this algorithm is a pair of coordinates, the endpoints of the line, and as result, the set of points that completes the line between, is returned.
%\todo{Check bresenham algorithm reference}

As the output, this block generates an occupancy grid of the scene, which is published at a rate defined by the previous period $T_{om}$.
%\todo{update policy}

@@

The purpose of this block is to detect the vehicles from the streaming of video from a camera. To accomplish this task, the YOLOv3 detection system \cite{yolov3} was wraped into a block. The algorithm used by this detector, applies a single neural network to the full image. This network divides the image into regions and predicts bounding boxes and probabilities for each region. These bounding boxes are weighted by the predicted probabilities. The output of this block, are the bounding boxes with high probabilty of being a vehicle.

@@

This block receives bounding boxes corresponding to vehicles and transform them from image coordinate system to the global reference system, Then, it maps the area covered by the boxes into an occupancuy grid in order to mark those cells as occupied in the same fashion as described for the block "points\_to\_occgrid" \ref{points_to_grid}.

@@

%\item[clusters\_to\_occupancy\_level] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
%\caption{clusters\_to\_occupancy\_level}
%\label{clusters_to_occupancy_level}
%\end{figure}

@@

%\item[occgrid\_to\_occupancy\_level] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
%\caption{occgrid\_to\_occupancy\_level}
%\label{occgrid_to_occupancy_level}
%\end{figure}

@@

\item[vehicle\_counter\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
\caption{vehicle\_counter\_merge}
\label{vehicle_counter_merge}
\end{figure}
%
%\item[occupancy\_level\_merge] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
%\caption{occupancy\_level\_merge}
%\label{occupancy_level_merge}
%\end{figure}

@@

\item[laser\_publisher] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/laser_publisher.pdf}
\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
\caption{laser\_publisher and camera\_publisher}
\label{sensors_publishers}
\end{figure}

These blocks are intended to read dataset files containing the information from the sensors and publish this data with the appropriate format and preserving the original rate of the sensors, if needed.

%\item[camera\_publisher] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
%\caption{camera\_publisher}
%\label{camera_publisher}
%\end{figure}

%\item[dataset\_control] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/dataset_ctrl.pdf}
%\caption{dataset\_control}
%\label{dataset_control}
%\end{figure}

@@

The objective of this block is to allow the visualisation of the data in any of the processing stages. It has the option to display and XY coordinate system, an occupancy grid or a map of the intersection overlaped with detections of metrics.

### 2018-06-21 ch4-results.tex
Minor modifications. Apendix removed
Final draft

The selected dataset testing the system is POSSi's \ref{possi_ds}. It contains 6 laser-scanners raw readings and a video from a camera located over the intersection. The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears. This groundtruth data was generated by human inspection.

\section{Test Configurations}
In order to test the proposed architecture, three different configurations have been selected. The first configuration is using just one laser sensor. The second configuration is based on multiple laser sensors, Finally, the third configuration uses multiple lasers along with a camera.

Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from sensors, lasers and cameras, to produce an output of higher level. In this case, vehicle counting is the metric used for evaluation.

@@

\subsection{Case 1: Single Laser}

@@

\subsection{Case 3: Multiple Lasers and camera}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
\caption{Multiple lasers and camera configuration}
\label{tconf3}
\end{figure}

>>>>

The selected dataset for testing the system is the one from POSSi project (section \ref{possi_ds}). It contains 6 laser-scanners raw readings and a video from a camera located over the intersection. The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears. This groundtruth data was generated manually.

\section{Test Configurations}
In order to test the proposed architecture, two different configurations have been selected. The first configuration is using just the camera information. The second configuration is based on multiple laser sensors along with the camera.

Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level. In this case, vehicle counting is the metric used for evaluation.

@@

\subsection{Case 1: Single Camera}

@@

%\subsection{Case 3: Multiple Lasers and camera}
%
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
%\caption{Multiple lasers and camera configuration}
%\label{tconf3}
%\end{figure}

### 2018-06-21 ch5-conclusions.tex
Final draft

Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.

@@

Another contribution is a comprehensive review on intersection management systems, including a classification scheme based on its components and its main application. This could serve to readers as an introductory resource on how has been the evolutions of those systems and what is the future of them.

@@

On the other side, a couple of articles are being reviewed previous to be submmited to journal. One article is for architecture description and example implementation and another for application comparison.

@@

Integration with other technologies and new trends. At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefulness and relevance of these projects in real deployements. It is important that new versions of the system will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.

>>>>

Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, it is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.

@@

Another contribution is a comprehensive review on intersection management systems, including a classification scheme based on its components and its main application. This could serve to readers as an introductory resource on how such systems have been evolving and what is the future of them.

@@

On the other side, a couple of articles are being reviewed previous to be submmited to a journal. One article is for architecture description and example implementation and another for application comparison.

@@

Integration with other technologies and new trends. At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefulness and relevance of this kind of projects in real deployements. It is important that new versions of the system will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.

### 2018-06-21 main.tex
Updated bibliography. Changed bibliography style
Created draft for chapter 3
Some corrections and modifications
Updated bibliography and redesigned figure 2.5 to a table
Finished table of fusion models.
Fusion algorithms section finished. Enhancement in tables. Included enumitem package.
Some corrections and parragraph added to ch2. conclusions
Created a draft for the structure of Chapter 3
Added list of figures and tables. Corrected some typos.
Inlcuded package for bookmarks. Updated .gitignore
Added third IMS component paragraph, Target
Added packages for multipage tables
Semi-Finished chapt

\usepackage[utf8]{inputenc}
%\usepackage[spanish]{babel}
%\usepackage[spanish]{isodate}
\usepackage[final]{listings}
\usepackage{courier}

\usepackage[pdftex]{graphicx}

%\renewcommand{\chaptername}{Capítulo}
\renewcommand{\figurename}{Figure}

@@

@@

\title{Multisensor Architecture for an Intersection Management System}
\author{Gustavo Velasco-Hernández}
\date{\today}
\maketitle

@@

\input{ch1-introduction}
\input{ch2-mdf_ims}
%\input{CH3-ES}

\bibliographystyle{plain}
\bibliography{bibliography}

>>>>

\usepackage[utf8]{inputenc}
%\usepackage[spanish]{babel}
%\usepackage[spanish]{isodate}
\usepackage[final]{listings}
\usepackage{courier}
\usepackage{multirow}
\usepackage{enumitem}
% For links
\usepackage[bookmarks]{hyperref}
\hypersetup{colorlinks=true,allcolors=blue}

\usepackage[pdftex]{graphicx}
\usepackage[toc,page]{appendix}
\usepackage[nottoc]{tocbibind}

\usepackage{longtable}
\usepackage{pbox}
%\usepackage[sorting=none]{biblatex}
\usepackage{gensymb}
\usepackage{epigraph}

\usepackage{todonotes}

\usepackage{titling}
\usepackage{setspace}

\def\arraystretch{1.1}

%\renewcommand{\chaptername}{Capítulo}
%\renewcommand{\figurename}{Figure}

@@

\bibliographystyle{abbrv}
%\bibliographystyle{apalike}

\hyphenation{detection camera cameras Systems}

@@

\input{title1}
\input{title2}

%\title{Multisensor Architecture for an Intersection Management System\vspace{8cm}}
%\vfill
%\vfill
%\vfill
%\author{Gustavo Velasco-Hernandez\vspace{5cm}}
%\date{\today}
%\maketitle
%
%\title{Multisensor Architecture for an Intersection Management System}
%\vfill
%\vfill
%\vfill
%\author{Gustavo Velasco-Hernandez}
%\vfill
%\vfill
%\vfill
%\date{\today}
%\maketitle

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}%
Intersections or juntions are critical points in transportation systems due to their dynamic nature, making them prone to safety or efficiency problems. For this reason the use of technology in monitoring intersections have been increasing over the last years. After a comprehensive review on this topic, a  multisensor architecture for an intersection management system is conceived, having as main features its scalability and modularity. This architecture is composed by 4 main elements: communication structure, data model, information structure and processing blocks. An example implementation of the architecture is made using the publisher/subscriber approach along with different tools and technologies that allow the whole system to fulfill the proposed criteria, to be scalable and modular. After testing the system using a dataset containing data from camera sensors and lasers sensors, some comments about its results, future developments and integration with current needs and new trends, are discussed.

%\chapter*{Acknowledgements}%
%\addcontentsline{toc}{chapter}{Acknowledgements}%

%I would like to thank to all people that in some way or another BLABLABLA

@@

\listoffigures

\listoftables

\input{ch1-introduction}

\include{ch2-mdf_ims}

\include{ch3-arch_sys}

\include{ch4-results}

\include{ch5-conclusions}

%\begin{appendices}
%	\chapter {Vehicular Environment Simulators}
%\end{appendices}

\bibliography{bibliography}
%\bibliography{ref}

### 2018-06-21 title2.tex
Replaced \maketitle with titlepages
Minor modifications. Apendix removed
Final draft

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
        \Huge

        Multisensor Architecture for an Intersection Management System

        \vspace{4.5cm}
        \LARGE
        Gustavo Adolfo Velasco-Hernandez

        \vfill
        \large
        \vspace{0.8cm}

        %\includegraphics[width=0.4\textwidth]{university}

        School of Electrical and Electronics Engineering\\
        Universidad del Valle\\
        Colombia\\
        \today

>>>>

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
        \Huge        
        Multisensor Architecture for an Intersection Management System

        \vspace{3.5cm}
        \LARGE
        Gustavo Adolfo Velasco-Hernandez

        \vfill
        \large

        A thesis presented in partial fulfillment of the Requirement for the degree of Master of Science in Engineering with emphasis on Electronics.

        \vspace{2cm}

        Advisor: Prof. Eduardo Caicedo Bravo

		\vspace{2cm}

        %\includegraphics[width=0.4\textwidth]{university}
        Perception and Intelligent Systems Research Group \\
        School of Electrical and Electronics Engineering\\
        Universidad del Valle\\
        Colombia\\
        \today
